A Few Easy Pieces: \\ How to enhance your relationship with your future self.

### 2011-03-14 workflow.Rnw
Colored links
Moving comments earlier in the document.
Subsequent sections refer to commenting code, so I think it makes
sense to move it up in the outline. This change also suggests moving
around other sections.

\documentclass[12pt]{article}
\usepackage{fancyvrb,natbib,url,array,dcolumn,float,booktabs,listings}
\usepackage{hyperref}

@@

Just in case one has some doubt about answering these questions, this
piece aims to amplify some of what we already ought to know from
\citet{nagler1995coding} and \citet{king1995replication}, and to
update some of those ideas given current practices, platforms, and
propensities.

@@

All files containing commands operating on data must refer to a data
file. A reference to a data file is a line of code the analysis
program will use to operate on (``load''/ ``open'' / ``get'' /
                                ``use'') the data file. One should not have to edit this line on
different computers or platforms in order to execute this command.
Using R, for example, all analysis files should have
load('thedata.rda') or
\Verb+read.csv('http://www.mywebsite.org/Data/thedata.csv')+ or some
equivalent line in them, and 'thedata.csv' should be stored in some
place easy to find (like in the same directory as the file or perhaps
                    in 'Data/thedata.rda').

@@

good.df<-na.omit(dem.nations.df[,c("Gini2004","protac2000","Nation","meanpr")])
@

@@

\section{No data analyst is an island.}

Read \citet{nagler1995coding}. Comment your code. Luckily, if you are
using a literate programming practice (Sweave, odfWeave, using R2HTML,
etc..), you can write paragraphs to surround your code as well a
technical comments in the code itself. If you are not using a strictly
literate programming practice then use whatever commenting protocol
exists in your analysis language.

>>>>

\documentclass[12pt]{article}
\usepackage{fancyvrb,natbib,url,array,dcolumn,float,booktabs,listings}
\usepackage[colorlinks=TRUE]{hyperref}

@@

Just in case one has some doubt about answering these questions, this
piece aims to amplify some of what we already ought to know from
\citet{nagler1995coding} and \citet{king1995replication}, and to
update some of those ideas given current practices, platforms, and
propensities

%%% This data frame will be used throughout the analyses.
%%% Putting it up top, so we can use it in the comments section.

good.df<-na.omit(dem.nations.df[,c("Gini2004","protac2000","Nation","meanpr")])
@.

\section{No data analyst is an island.}
% MMF: My original title before I saw you had you own comment section
% \section{Comment on your own work. }

Comments, or text inside of a file that is not executed, are a message to your
future self and other consumers of your work. 
Read \citet{nagler1995coding}. Comment your code. Luckily, if you are
using a literate programming practice (Sweave, odfWeave, using R2HTML,
etc..), you can write paragraphs to surround your code as well a
technical comments in the code itself. If you are not using a strictly
literate programming practice then use whatever commenting protocol
exists in your analysis language. Here are some examples:
\begin{verbatim}
# This is a comment in R.
# With a a second line.

* This is a comment in a Stata .do file
* You can also embed comments at the ends of lines using /* ... */

/* SAS uses a similar convention to Stata
   and allows multi-line comments like this.
*/

% Finally, the percent symbol is a comment in TeX.
\end{verbatim}

Comment liberally. Comments are discarded when R runs analysis or LaTeX turns
your poignant writings into a PDF, so only those who dig into your work will
see them. They are footnotes on the process of producing your research.

@@

All files containing commands operating on data must refer to a data
file. A reference to a data file is a line of code the analysis
program will use to operate on (``load''/ ``open'' / ``get'' /
                                ``use'') the data file. One should not have to edit this line on
different computers or platforms in order to execute this command.
Using R, for example, all analysis files should have
load('thedata.rda') or
\Verb+read.csv('http://www.mywebsite.org/Data/thedata.csv')+ or some
equivalent line in them, and 'thedata.csv' should be stored in some
place easy to find (like in the same directory as the file or perhaps
                    in 'Data/thedata.rda').
It never hurts to drop in a comment about where the data is, if in doubt.

@@

@@
